An Open-Source Repository of Real-Time COVID-19 Indicators

### 2021-06-12 indicators/paper/paper.tex
Small language tweak

For many purposes it is sufficient to know the most recently issued observation
for any time value, and the COVIDcast API reports the most recent issue by
default. However, for some purposes it is crucial to know what was known
\textit{as of} a specific date. For example, an epidemic forecasting model will
be called upon to make its forecasts based on preliminary data about recent
trends, and so when it is trained using historical data, it should be trained
using the initial versions of that data, not updates that would have been
received later. Furthermore, these revision records allow models to be modified
to account for noise and bias in early data versions, or to exclude data that is
too new to be considered stable, and to ``rewind'' time and simulate how these
revised models would have performed using only the versions of data available
\textit{as of} those times.

>>>>

For many purposes it is sufficient to use the most recently issued observation
for any time value, and thus the COVIDcast API reports the most recent issue by
default. However, for some applications it is crucial to know what was known
\textit{as of} a specific date. For example, an epidemic forecasting model will
be called upon to make its forecasts based on preliminary data about recent
trends, and so when it is trained using historical data, it should be trained
using the initial versions of that data, not updates that would have been
received later. Furthermore, these revision records allow models to be modified
to account for noise and bias in early data versions, or to exclude data that is
too new to be considered stable, and to ``rewind'' time and simulate how these
revised models would have performed using only the versions of data available
\textit{as of} those times.
